Designing a high-performance boundary element library with OpenCL and Numba

### 2021-04-13 intro.tex

Boundary element methods are particularly suited to this library model, as the main performance critical task is the computation of discrete operators. Once fast kernels for this have been implemented, the remaining functionality of the library can be written entirely in Python without any great detriment to performance.

>>>>

Boundary element methods are particularly suited to this library model, as the main performance critical task is the computation of discrete operators. Once fast kernels for this have been implemented, the remaining functionality of the library can be written entirely in Python without any great decrease in performance.
